\tb{Place of Residence and Political Attitudes in Democracies Worldwide \\ {\large Online Appendix C -- Margins Plots} }

### 2018-12-10 Online Appendices/Appendix C.tex
Margins Plots

\title{\tb{Place of Residence and Political Attitudes in Democracies Worldwide \\ {\large Online Appendix A -- Box Plots} }}

@@

This Appendix features the box plots for each country divided by place of residence and by dependent variable.

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
	\centering 
	\includegraphics[width=\textwidth]{IdeoBP/Austria}
	\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
	\centering 
	\includegraphics[width=\textwidth]{BoxLib/Austria}
	\caption{Issue Stances}
	\end{subfigure}
	\caption{Austria}
	\label{Austria}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Bulgaria}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Bulgaria}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Bulgaria}
	\label{Bulgaria}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Czech}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Czech}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Czech Republic}
	\label{Czech}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Finland}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Finland}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Finland}
	\label{Finland}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/France}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/France}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{France}
	\label{France}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Germany}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Germany}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Germany}
	\label{Germany}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Greece}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Greece}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Greece}
	\label{Greece}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Iceland}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Iceland}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Iceland}
	\label{Iceland}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Israel}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Israel}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Israel}
	\label{Israel}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Japan}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Japan}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Japan}
	\label{Japan}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Latvia}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Latvia}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Latvia}
	\label{Latvia}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Mexico}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Mexico}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Mexico}
	\label{Mexico}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Montenegro}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Montenegro}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Montenegro}
	\label{Montenegro}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/NewZealand}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/NZealand}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{New Zealand}
	\label{NewZealand}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Peru}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Peru}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Peru}
	\label{Peru}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Philippines}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Philipines}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Philippines}
	\label{Philippines}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Poland}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Poland}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Poland}
	\label{Poland}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Romania}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Romania}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Romania}
	\label{Romania}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/SouthAfrica}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/SAfrica}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{South Africa}
	\label{SouthAfrica}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/SouthKorea}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/SKorea}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{South Korea}
	\label{SouthKorea}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Sweden}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Sweden}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Sweden}
	\label{Sweden}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeoBP/Turkey}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{BoxLib/Turkey}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Turkey}
	\label{Turkey}
\end{figure}

>>>>

\title{\tb{Place of Residence and Political Attitudes in Democracies Worldwide \\ {\large Online Appendix C -- Margins Plots} }}

@@

\section{The Regressions}

The regressions for this model are based on the worldwide trends to better understand how a regime's level of democracy, electoral formula and regime age influence the relationship of the people's place of residence and political attitudes. In addition to these macro variables of interest in the third hypothesis of the main paper, the country's Freedom House rating and Corruption Perception Index score were also added as a means to understanding whether these factors influence the key independent and dependent variables in the analysis.

The following codes were used to run the regressions in Stata Version 15.1. Each variable name is not exactly to what was used due to renames and recodes after the data cleaning process. The variable names included throughout all appendices are used to aid in understanding of the process and connecting the variables used to their descriptions in the CSES Module IV codebook.

\section{The Margins Plots}
